Reanalysis Step 2: Multiple Imputation

### 2025-08-19 reanalysis-2-multiple_imputation.qmd
style

```{r run-imputation}
# Set seed for reproducibility
set.seed(2025)

# Run mice imputation
# Note: Parameters are set based on analysis_mode in setup
message("Starting multiple imputation...")
message("Mode: ", analysis_mode)
message("Imputations: ", n_imputations)
message("Iterations: ", n_iterations)

@@

```{r save-imputed}
# Save mice object for later use
saveRDS(mice_results, file.path(reanalysis_data_dir, "mice_results.rds"))

# Save list of complete imputed datasets
saveRDS(imputed_datasets, file.path(reanalysis_data_dir, "imputed_datasets.rds"))

# Save first imputed dataset separately for testing
saveRDS(imputed_datasets[[1]], file.path(reanalysis_data_dir, "imputed_dataset_1.rds"))

message("Saved ", n_imputations, " imputed datasets to: ", reanalysis_data_dir)
```

@@

```{r summary}
# Summary of imputation
summary_table <- tibble(
  Metric = c(
    "Original observations",
    "Variables in imputation model",
    "Variables with missing data",
    "Number of imputations",
    "Maximum missing percentage",
    "Imputation iterations"
  ),
  Value = c(
    nrow(df_mice),
    ncol(df_mice),
    sum(mice_results$nmis > 0),
    n_imputations,
    paste0(round(max(mice_results$nmis/nrow(df_mice)) * 100, 1), "%"),
    mice_results$iteration
  )
)

@@

# Variables that were imputed
imputed_vars <- names(mice_results$nmis)[mice_results$nmis > 0]
message("Variables that were imputed:")
print(imputed_vars)
```

>>>>

```{r run-imputation}
# Run mice imputation
# Note: Parameters are set based on analysis_mode in setup
message("Starting multiple imputation...")
message("Mode: ", analysis_mode)
message("Imputations: ", n_imputations)
message("Iterations: ", n_iterations)

@@

```{r save-imputed}
saveRDS(mice_results, file.path(reanalysis_data_dir, "mice_results.rds"))
saveRDS(imputed_datasets, file.path(reanalysis_data_dir, "imputed_datasets.rds"))
saveRDS(imputed_datasets[[1]], file.path(reanalysis_data_dir, "imputed_dataset_1.rds"))
message("Saved ", n_imputations, " imputed datasets to: ", reanalysis_data_dir)
```

@@

```{r summary}
summary_table <- tibble(
  Metric = c(
    "Original observations",
    "Variables in imputation model",
    "Variables with missing data",
    "Number of imputations",
    "Maximum missing percentage",
    "Imputation iterations"
  ),
  Value = c(
    nrow(df_mice),
    ncol(df_mice),
    sum(mice_results$nmis > 0),
    n_imputations,
    paste0(round(max(mice_results$nmis/nrow(df_mice)) * 100, 1), "%"),
    mice_results$iteration
  )
)

@@

imputed_vars <- names(mice_results$nmis)[mice_results$nmis > 0]
message("Variables that were imputed:")
print(imputed_vars)
```
